\Title

### 2020-03-16 manuscript/manuscript.tex
Replace block median for block averaged

\begin{enumerate}
    \item Dividing the region in blocks of equal size. The size of the blocks
        is controlled by a \emph{spacing} parameter.
        (see Fig.~\ref{fig:block-median-sources}(a)-(b)).
    \item Computing the median location of the observation points that fall
        inside each block. Blocks without any observation point are ignored.
    \item Locating one point source below each block averaged coordinate.
        (see Fig.~\ref{fig:block-median-sources}(c)).
\end{enumerate}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
    \caption{
        Block averaged sources.
        (a)~Given a set of observation points
        (b)~we divide the survey region on blocks of equal size and compute the
            median location of the observation points that fall inside each
            block.
        (c)~A source point is located beneath each block averaged coordinate.
            The number of point sources could be less or equal to the number of
            observation points. No source is located beneath unpopulated
            blocks.
    }
    \label{fig:block-median-sources}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
            obtained through the \emph{sources beneath data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

@@

Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey} also show the parameter combination
that produces the best prediction for each source distribution and its
corresponding R$^2$ score, for both ground and synthetic surveys, respectively.
Figures~ \ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution, for
both ground and synthetic surveys, respectively.

@@

Figures~ \ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show that all source distributions
produce accurate predictions, both for the ground and airborne survey.
The R$^2$ scores don't show significant difference, so we can only conclude
that all the source distributions are able to produce comparable predictions.
Nevertheless, the \emph{block averaged sources} make use of less sources to
produce this predictions, what would reduce the computational load needed to
fit the sources coefficients and finally compute the actual prediction.

@@

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesConstantDepthDepth
                  \GroundBlockMedianSourcesConstantDepthDepthIncrement
                & \BestGroundBlockMedianSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockMedianSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement
                & \BestGroundBlockMedianSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                  \GroundBlockMedianSourcesConstantDepthDampingIncrement
                & \BestGroundBlockMedianSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement
                & \BestGroundBlockMedianSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockMedianSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement
                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement
                & \BestGroundBlockMedianSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesVariableDepthDepth
                  \GroundBlockMedianSourcesVariableDepthDepthIncrement
                & \BestGroundBlockMedianSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockMedianSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement
                & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement
                & \BestGroundBlockMedianSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement
                & \BestGroundBlockMedianSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                  \GroundBlockMedianSourcesVariableDepthDampingIncrement
                & \BestGroundBlockMedianSourcesVariableDepthDamping
                & \\
        \midrule

@@

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement
                & \BestAirborneBlockMedianSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockMedianSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement
                & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement
                & \BestAirborneBlockMedianSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockMedianSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement
                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement
                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockMedianSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthDamping
                & \\
        \midrule

>>>>

\begin{enumerate}
    \item Dividing the region in blocks of equal size. The size of the blocks
        is controlled by a \emph{spacing} parameter.
        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
    \item Computing the median location of the observation points that fall
        inside each block. Blocks without any observation point are ignored.
    \item Locating one point source below each block averaged coordinate.
        (see Fig.~\ref{fig:block-averaged-sources}(c)).
\end{enumerate}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-averaged-sources-schematics.pdf}
    \caption{
        Block averaged sources.
        (a)~Given a set of observation points
        (b)~we divide the survey region on blocks of equal size and compute the
            median location of the observation points that fall inside each
            block.
        (c)~A source point is located beneath each block averaged coordinate.
            The number of point sources could be less or equal to the number of
            observation points. No source is located beneath unpopulated
            blocks.
    }
    \label{fig:block-averaged-sources}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
            obtained through the \emph{sources beneath data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockaveragedSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

@@

Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey} also show the parameter combination
that produces the best prediction for each source distribution and its
corresponding R$^2$ score, for both ground and synthetic surveys, respectively.
Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution, for
both ground and synthetic surveys, respectively.

@@

Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show that all source distributions
produce accurate predictions, both for the ground and airborne survey.
The R$^2$ scores don't show significant difference, so we can only conclude
that all the source distributions are able to produce comparable predictions.
Nevertheless, the \emph{block averaged sources} make use of less sources to
produce this predictions, what would reduce the computational load needed to
fit the sources coefficients and finally compute the actual prediction.

@@

        \multirow{11}{*}{Block averaged sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesConstantDepthDepth
                  \GroundBlockAveragedSourcesConstantDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesConstantDepthSpacing
                  \GroundBlockAveragedSourcesConstantDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesConstantDepthDamping
                  \GroundBlockAveragedSourcesConstantDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesRelativeDepthDepth
                  \GroundBlockAveragedSourcesRelativeDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesRelativeDepthSpacing
                  \GroundBlockAveragedSourcesRelativeDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesRelativeDepthDamping
                  \GroundBlockAveragedSourcesRelativeDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesVariableDepthDepth
                  \GroundBlockAveragedSourcesVariableDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockAveragedSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
                  \GroundBlockAveragedSourcesVariableDepthDepthFactorIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundBlockAveragedSourcesVariableDepthKNearest
                  \GroundBlockAveragedSourcesVariableDepthKNearestIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesVariableDepthSpacing
                  \GroundBlockAveragedSourcesVariableDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesVariableDepthDamping
                  \GroundBlockAveragedSourcesVariableDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

@@

        \multirow{11}{*}{Block averaged sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesConstantDepthDepth
                  \AirborneBlockAveragedSourcesConstantDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesConstantDepthSpacing
                  \AirborneBlockAveragedSourcesConstantDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesConstantDepthDamping
                  \AirborneBlockAveragedSourcesConstantDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesRelativeDepthDepth
                  \AirborneBlockAveragedSourcesRelativeDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
                  \AirborneBlockAveragedSourcesRelativeDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesRelativeDepthDamping
                  \AirborneBlockAveragedSourcesRelativeDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesVariableDepthDepth
                  \AirborneBlockAveragedSourcesVariableDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockAveragedSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
                  \AirborneBlockAveragedSourcesVariableDepthDepthFactorIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneBlockAveragedSourcesVariableDepthKNearest
                  \AirborneBlockAveragedSourcesVariableDepthKNearestIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesVariableDepthSpacing
                  \AirborneBlockAveragedSourcesVariableDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesVariableDepthDamping
                  \AirborneBlockAveragedSourcesVariableDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule
